A boundary-integral framework to simulate \\ the viscous erosion of a porous medium

### 2018-04-06 docs/methods/erosion_methods.tex
small changes

\begin{abstract} 
We develop numerical methods to simulate the fluid-mechanical erosion of
many bodies in a two-dimensional Stokes flow. The broad aim
is to simulate the erosion of a porous medium (e.g.~ground water flow)
with grain-scale resolution. Our fluid solver is based on a
second-kind boundary integral formulation of the Stokes equations that is
discretized with a spectrally-accurate Nystr\"om method and solved
with a fast-multipole-accelerated GMRES iteration. To evolve the individual grains under shear-driven
erosion, we regularize via curvature-penalization and solve the
associated system using the {\thL} formulation. This framework allows
numerically stable treatment of stiff terms, thus permitting large time
steps. The overall accuracy of our method is exponential in space and
second-order in time. The method is computationally efficient, with the
fluid solver requiring $\mathcal{O}(N)$ operations per GMRES iteration,
a mesh-independent number of GMRES iterations, and a one-time
$\mathcal{O}(N^2)$ computation to compute the shear stress. We benchmark single-body results against analytical predictions. In our multibody simulations, we find that erosion leads to spontaneous channelization between bodies in near contact. The channelization is associated with a dramatic reduction in the resistance of the porous medium, much more than would be expected from the reduction in grain size alone.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction\label{s:intro}}

Flow-induced erosion deteriorates and reshapes solid material over a range of scales found in nature, from large geological formations \cite{han1969, Rothman2012, coh-dev-sey-yi-szy-rot2015}, down to human-scale features and patterns \cite{daerr2003erosion}. Though less visible, these same forces are at work at the very smallest scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay) or biological structures like plaque and biofilms \cite{pic-van-hei2000, sha2002, gro-gij-van-fer-hat-van-yua-wen2007}. Motivated by such applications, we develop here numerical methods to simulate fluid-mechanical erosion of multiple solid bodies in Stokes flow --- the most relevant regime for groundwater and bio-fluid applications.

Recent work in the high-Reynolds regime has highlighted the importance of the feedback between flow and morphology that occurs during erosion \cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, hewett2017evolution, moore2017riemann}, and a similar feedback occurs in the related processes of dissolution and melting \cite{Huang2015, kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion, hewett2017pear, claudin2017dissolution}. In such cases, the flow alters the shape of the immersed structures, which in turn modifies the surrounding flow, and so on. Collectively, such processes have been referred to as `sculpting with flow'~\cite{ristroph2018sculpting}. From this viewpoint, the example of an eroding porous medium presents a new opportunities and challenges. First, the medium itself is composed of many solid constituents, and so multi-body interactions, especially close interactions, must be considered. Second, the long-range interactions facilitated by Stokes flow even more strongly couples the shape evolution of neighboring bodies, making their interactions even more important.

\paragraph{Contributions}
The methods developed here will allow us to simulate the erosion of many bodies, as demonstrated in Fig.~\ref{fig:50bodies} for the case of 50 bodies (of randomly assigned initial sizes and positions). Here, the erosion of solid material arises from the mechanical stress induced by the surrounding flow. In particular, we take the local rate of erosion to be proportional to the magnitude of the shear stress -- a law that has been verified by laboratory experiments \cite{ris-moo-chi-she-zha2012}. As seen in the figure, erosion not only diminishes the size of the bodies, but also alters their shapes considerably. Notice, in particular, that many bodies develop corner-like features and nearly flat faces, with straight channels intervening between them. In the figure, color represents the vorticity of the surrounding flow, which reduces to shear on solid boundaries and thus provides a convenient tool for visualizing local erosion rates.

@@

To evolve the boundaries of eroding bodies, we use the {\thL} framework which offers certain advantages in the ability to numerically stabilize moving-interface problems \cite{hou-low-she1994}. Here, $\theta$ is the local tangent angle and $L$ is the total perimeter of a given boundary. For a boundary parametrized by arclength $(x(s),y(s))$, the local tangent angle is defined through the relation $\left( \pdi{x}{s}, \pdi{y}{s} \right) = \left(\cos \theta, \sin \theta \right)$.

@@

The boundary of each body will be represented by a grid of collocation
points. If we were to simply evolve the interfaces
under~\eqref{eqn:Vn2}, this grid would become distorted, which, if
unchecked, could lead to severe tangling and numerical instability. We
therefore introduce an artificial tangential velocity $\Vs$ to keep the grid points equally spaced in arclength \cite{hou-low-she1994}. The appropriate tangential velocity satisfies 
\begin{align}
\pderiv{\Vs}{\alpha} = \thalpha \Vn - \mean{\thalpha \Vn} \, .
\end{align}
The evolution of the interface is then given by the combination of the normal and tangential velocity
\begin{align}
\dot{\xx}(t) = \Vn \nn + \Vs \ss \, .
\end{align}
Since $\Vs$ is tangential, it does not modify the physics of erosion, only the parameterization of the boundaries.

@@

Figure~\ref{shrink_intface}(a) shows that the spacing between successive interfaces becomes larger with time, suggesting that the overall shear stress grows as the body vanishes. This observation is consistent with the well-known 3D Stokes drag law, in which stress, $\tau \sim \mu \umax / a$, scales inversely proportional to body-scale $a$ (e.g.~for a sphere, $a$ is the radius). This law must be modified in two dimensions, though. The modification is made non-trivial by subtleties of the 2D Stokes paradox, but can be correctly deduced by noting that, as the body vanishes, its drag must be consistent with slender-body theory \cite{batchelor1970slender, MooreJFM2012}. 
For a slender body in flow perpendicular to its long-axis $\ell$, the drag is proportional to
$\mu \umax \ell/ \log(\ell/a)$, where $a \ll \ell $ is a length scale of the cross-section. This law implies that the stress-per-unit-span on a 2D cross-section is approximately
\begin{align}
  \label{eqn:stresslaw}
  \tau \sim \frac{\mu \umax}{a \log(\ell/a)} \qquad \text{for } a \ll \ell \, .
\end{align}
In interpreting our 2D simulations, we will treat the span, $\ell$, as
fixed. Recall that $L$ denotes the total perimeter of the 2D cross-section. Since $L$ and $a$ each represent a characteristic scale of the cross-section, they can often be interchanged in scaling analysis.

@@

With the vanishing rate understood, we now seek to quantify the limiting shape observed in Fig.~\ref{shrink_intface}(a). In particular, consider the corner formed at the front and rear of the body. Locally, we can neglect body curvature and consider the problem of Stokes flow around an infinite wedge; see Fig.~\ref{corner} for a schematic. We seek to predict the wedge's opening angle, $\oangle$, by appealing to the principle that, in long time, erosion uniformly distributes the shear stress along the surface \cite{moo-ris-chi-zha-she2013, moore2017riemann}. For a wedge of arbitrary angle, the surrounding flow can be determined exactly in polar coordinates $(r, \theta)$ where $\theta \in [-\thb,\thb]$ and $\thb = \pi - \oangle/2$ (in this section alone, $\theta$ denotes the polar coordinate and not the local tangent angle).

@@

	We show in Fig.~\ref{fixed_intface}(a) several interfaces of this modified erosion process, with the same spatial resolution, $N_\iin = 1024$, as before. Notice the body obtains a similar profile as observed previously, but now with fixed area. Importantly, more numerical accuracy is available to quantify the terminal state. The inset in Fig.~\ref{fixed_intface}(a) zooms on the rear corner demonstrate that, due to our numerical regularization, the body is actually smooth on a fine scale. We show in Fig.~\ref{fixed_intface}(b) the stress distributions on the same interfaces. As observed previously, the stress becomes more evenly distributed as erosion reshapes the body. The slight rise in shear near the front/rear corners that was observed in Fig.~\ref{shrink_intface}(b) is no longer present, suggesting that this effect was due to loss of accuracy. Rather, the late-time stress distributions in Fig.~\ref{fixed_intface}(b) decrease monotonically to zero near the stagnation points. In this figure, time is normalized by the vanishing time $t_f = 1.79 \times 10^{-2}$ from the shrinking simulations (i.e.~Fig.~\ref{shrink_intface}). Curiously, about 3 multiples of $t_f$ are required to reach a visible steady state, which contrasts with previous studies on high-Reynolds-number erosion in which a steady state usually emerged before the body disappeared \cite{moo-ris-chi-zha-she2013}.

@@

	In summary, we have found that a single-body eroding in 2D Stokes flow converges to a terminal form characterized by nearly uniform shear stress along its surface. The final shape is fairly slender, with an aspect ratio of 2.7, and distinguished by  corners of opening angle $102^{\circ}$ at the front and rear. This shape is closely related to the drag-minimizing profile found by Pironneau (1973) --- the geometry that minimizes drag in 3D Stokes flow subject to the constraint of fixed volume \cite{pir1973}. Using variational principles, Pironneau showed that the drag-minimizing form has constant shear (or vorticity) along its surface. The resulting {\em axisymmetric} shape has an aspect ratio of 2.1 and front/rear opening-angles of $120^{\circ}$ \cite{pir1973, mit-spa2016}. Interestingly, 3D simulations of viscous erosion showed close resemblance between the shape formed by a single eroding body and this Pironneau form \cite{mit-spa2016}. It was found that the eroding body does not converge {\em precisely} to the Pironneau shape because the long-time surface-stress distribution created by erosion is only {\em approximately} uniform. Rather than strict uniformity, variations in body curvature must be offset by slight variations in $\Vn$ for self-similar reduction \cite{pir1973, mit-spa2016}. Pironneau's argument that the drag-minimizing form has constant surface stress applies to 2D as well. Therefore, the shape observed in our simulation is approximately the form that minimizes drag subject to fixed area, i.e.~the 2D counterpart to Pironneau's shape. How close this shape is to the true drag-minimizer is related to how close the stress distributions are to uniform, as can be seen in Fig.~\ref{shrink_intface}(b).

@@

\section{Results: Multibody erosion}
\label{s:MultiResults}

@@

Briefly, to validate the multibody simulations with this new fixed-pressure-drop condition, we report a convergence test in Table \ref{convtab}. In this test, we simulate the erosion of 20 bodies to a stopping time of $t_s = 4 \times 10^{-3}$. This stopping time is 24\% of the time required for {\em all} bodies to vanish, and, in fact, a few of the bodies will have already vanished by $t_s$. To assess error, we measure the aggregate $L^2$-difference in the shape of {\em all} of the bodies, comparing simulations of successive temporal resolution. Note that this metric is sensitive to numerical errors in any of the simulated bodies. The table confirms that our method retains second-order accuracy in time, thus validating our rescaling procedure and confirming that multibody interactions are handled correctly by the Stokes solver. The last column of the table shows the computational time of each simulation, demonstrating a linear increase with temporal resolution. Naturally, these 20-body simulations require significantly more CPU time than do the single-body simulations.

@@

\subsection{Multibody results}

With the validation complete, we now discuss the emergent physics of multibody erosion revealed by our simulations. We begin with a relatively simple case of 6 eroding bodies, as this will allow us to identify key principles at work in more complex cases (e.g.~the 50-body simulation in Fig.~\ref{fig:50bodies}). Figure~\ref{fig:06bodies} shows the simulated erosion of 6 bodies, each initial circles of various sizes and positions. Over time, erosion not only diminishes the size of the bodies, but also alters their shapes considerable. As in the single-body simulations, corner-like features develop, but not in locations that are easily predictable. Rather, when and where these corners form depends on how neighboring bodies interact with one another as mediated by the Stokes flow.

@@

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.90 \textwidth]{./figs/mbodyplots.pdf}
\caption{\label{fig:mbodyplots} 
Multibody simulation results: black curves correspond to the 6-body simulation and gray to the 50-body simulation. (a) The area fraction of the eroding bodies versus time. (b) The incoming flow rate $\umax$ versus time. The fixed-pressure-drop condition causes $\umax$ to increase as bodies erode. (c) The total drag exerted by all bodies. Because $\umax$ increases as the bodies erode, the drag remains nearly constant throughout much of the simulation. In the very last moments, the drag drops suddenly to zero. (d) Normalizing the drag by $\umax$ provides gives an estimate of how much resistance the porous matrix provides. The resistance decreases rapidly as the bodies erode.
}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Figure generated from data file 50circ512p5, 
%which uses 50circ512.in with epsfac = 30, sigfac = 10, dt = 1e-4, fixpdrop = 1

To further quantify these observations, Fig.~\ref{fig:mbodyplots} shows several measurements taken from the multibody simulations. In all cases, the black curves correspond to the above 6-body simulation and gray curves to the 50-body simulation from Fig.~\ref{fig:50bodies}. First, Fig.~\ref{fig:mbodyplots}(a) shows the fraction of area occupied by the solid bodies as it varies in time. In the 6-body simulation, the initial configuration comprises about 40\% of the domain area, and this percentage steadily decreases as the bodies erode. The 50-body simulation shows a similar trend.

>>>>

\begin{abstract} 
We develop numerical methods to simulate the fluid-mechanical erosion of
many bodies in a two-dimensional Stokes flow. The broad aim
is to simulate the erosion of a porous medium (e.g.~ground water flow)
with grain-scale resolution. Our fluid solver is based on a
second-kind boundary integral formulation of the Stokes equations that is
discretized with a spectrally-accurate Nystr\"om method and solved
with a fast-multipole-accelerated GMRES. To evolve the individual grains under shear-driven
erosion, we regularize via curvature-penalization and solve the
associated system using the {\thL} formulation. This framework allows
numerically stable treatment of stiff terms, thus permitting large time
steps. The overall accuracy of our method is spectral in space and
second-order in time. The method is computationally efficient, with the
fluid solver requiring $\mathcal{O}(N)$ operations per GMRES iteration,
a mesh-independent number of GMRES iterations, and a one-time
$\mathcal{O}(N^2)$ computation to compute the shear stress. We benchmark
single-body results against analytical predictions. In our multi-body simulations, we find that erosion leads to spontaneous channelization between bodies in near contact. The channelization is associated with a dramatic reduction in the resistance of the porous medium, much more than would be expected from the reduction in grain size alone.
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction\label{s:intro}}
Flow-induced erosion deteriorates and reshapes solid material over a range of scales found in nature, from large geological formations~\cite{han1969, Rothman2012, coh-dev-sey-yi-szy-rot2015}, down to human-scale features and patterns~\cite{daerr2003erosion}. Though less visible, these same forces are at work at the very smallest scales, slowly deteriorating the individual constituents of porous media (e.g.~solid, sand, or clay) or biological structures like plaque and biofilms~\cite{pic-van-hei2000, sha2002, gro-gij-van-fer-hat-van-yua-wen2007}. Motivated by such applications, we develop numerical methods to simulate fluid-mechanical erosion of multiple solid bodies in Stokes flow --- the most relevant regime for groundwater and bio-fluid applications.

Recent work in the high-Reynolds number regime has highlighted the importance
of the feedback between flow and morphology that occurs during erosion~\cite{ris-moo-chi-she-zha2012, moo-ris-chi-zha-she2013, hewett2017evolution, moore2017riemann}, and a similar feedback occurs in the related processes of dissolution and melting~\cite{Huang2015, kondratiuk2015steadily, rycroft2016asymmetric, cohen2016erosion, hewett2017pear, claudin2017dissolution}. In such cases, the flow alters the shape of the immersed structures, which in turn modifies the surrounding flow, and so on. Collectively, such processes have been referred to as `sculpting with flow'~\cite{ristroph2018sculpting}. From this viewpoint, the example of an eroding porous medium presents new opportunities and challenges. First, the medium itself is composed of many solid constituents, so multi-body interactions, especially close interactions, must be considered. Second, the long-range interactions facilitated by Stokes flow even more strongly couples the shape evolution of neighboring bodies, making their interactions even more important.

\paragraph{Contributions}
The methods developed here will allow us to simulate the erosion of many bodies, as demonstrated in Fig.~\ref{fig:50bodies} for the case of 50 bodies (of randomly assigned initial sizes and positions). Here, the erosion of solid material arises from the mechanical stress induced by the surrounding flow. In particular, we take the local rate of erosion to be proportional to the magnitude of the shear stress --- a law that has been verified by laboratory experiments~\cite{ris-moo-chi-she-zha2012}. As seen in Fig.~\ref{fig:50bodies}, erosion not only diminishes the size of the bodies, but also alters their shapes considerably. Notice, in particular, that many bodies develop corner-like features and nearly flat faces, with straight channels intervening between them. In the figure, color represents the vorticity of the surrounding flow, which reduces to shear on solid boundaries and thus provides a convenient tool for visualizing local erosion rates.

@@

To evolve the boundaries of eroding bodies, we use the {\thL} framework which offers certain advantages in the ability to numerically stabilize moving-interface problems~\cite{hou-low-she1994}. Here, $\theta$ is the local tangent angle and $L$ is the total perimeter of a given boundary. For a boundary parametrized by arclength $(x(s),y(s))$, the local tangent angle is defined through the relation $\left( \pdi{x}{s}, \pdi{y}{s} \right) = \left(\cos \theta, \sin \theta \right)$.

@@

The boundary of each body will be represented by a grid of collocation
points. If we were to simply evolve the interfaces
under~\eqref{eqn:Vn2}, this grid would become distorted, which, if
unchecked, could lead to severe tangling and numerical instability. We
therefore introduce an artificial tangential velocity $\Vs$ to keep the grid points equally spaced in arclength~\cite{hou-low-she1994}. The appropriate tangential velocity satisfies 
\begin{align}
\pderiv{\Vs}{\alpha} = \thalpha \Vn - \mean{\thalpha \Vn} \, .
\end{align}
The evolution of the interface is then given by the combination of the normal and tangential velocity
\begin{align}
\dot{\xx}(t) = \Vn \nn + \Vs \ss \, .
\end{align}
Since $\Vs$ is tangential, it does not modify the physics of erosion, only the parameterization of the boundaries.

@@

Figure~\ref{shrink_intface}(a) shows that the spacing between successive interfaces becomes larger with time, suggesting that the overall shear stress grows as the body vanishes. This observation is consistent with the well-known 3D Stokes drag law, in which stress, $\tau \sim \mu \umax / a$, scales inversely proportional to body-scale $a$ (e.g.~for a sphere, $a$ is the radius). This law must be modified in two dimensions, though. The modification is made non-trivial by subtleties of the 2D Stokes paradox, but can be correctly deduced by noting that, as the body vanishes, its drag must be consistent with slender-body theory~\cite{batchelor1970slender, MooreJFM2012}. 
For a slender body in flow perpendicular to its long-axis $\ell$, the drag is proportional to
$\mu \umax \ell/ \log(\ell/a)$, where $a \ll \ell $ is a length scale of the cross-section. This law implies that the stress-per-unit-span on a 2D cross-section is approximately
\begin{align}
  \label{eqn:stresslaw}
  \tau \sim \frac{\mu \umax}{a \log(\ell/a)} \qquad \text{for } a \ll \ell \, .
\end{align}
In interpreting our 2D simulations, we will treat the span, $\ell$, as
fixed. Recall that $L$ denotes the total perimeter of the 2D cross-section. Since $L$ and $a$ each represent a characteristic scale of the cross-section, they can often be interchanged in scaling analysis.

@@

With the vanishing rate understood, we now seek to quantify the limiting shape observed in Fig.~\ref{shrink_intface}(a). In particular, consider the corner formed at the front and rear of the body. Locally, we can neglect body curvature and consider the problem of Stokes flow around an infinite wedge; see Fig.~\ref{corner} for a schematic. We seek to predict the wedge's opening angle, $\oangle$, by appealing to the principle that, in long time, erosion uniformly distributes the shear stress along the surface~\cite{moo-ris-chi-zha-she2013, moore2017riemann}. For a wedge of arbitrary angle, the surrounding flow can be determined exactly in polar coordinates $(r, \theta)$ where $\theta \in [-\thb,\thb]$ and $\thb = \pi - \oangle/2$ (in this section alone, $\theta$ denotes the polar coordinate and not the local tangent angle).

@@

	We show in Fig.~\ref{fixed_intface}(a) several interfaces of this modified erosion process, with the same spatial resolution, $N_\iin = 1024$, as before. Notice the body obtains a similar profile as observed previously, but now with fixed area. Importantly, more numerical accuracy is available to quantify the terminal state. The inset in Fig.~\ref{fixed_intface}(a) zooms on the rear corner demonstrate that, due to our numerical regularization, the body is actually smooth on a fine scale. We show in Fig.~\ref{fixed_intface}(b) the stress distributions on the same interfaces. As observed previously, the stress becomes more evenly distributed as erosion reshapes the body. The slight rise in shear near the front/rear corners that was observed in Fig.~\ref{shrink_intface}(b) is no longer present, suggesting that this effect was due to loss of accuracy. Rather, the late-time stress distributions in Fig.~\ref{fixed_intface}(b) decrease monotonically to zero near the stagnation points. In this figure, time is normalized by the vanishing time $t_f = 1.79 \times 10^{-2}$ from the shrinking simulations (i.e.~Fig.~\ref{shrink_intface}). Curiously, about 3 multiples of $t_f$ are required to reach a visible steady state, which contrasts with previous studies on high-Reynolds-number erosion in which a steady state usually emerged before the body disappeared~\cite{moo-ris-chi-zha-she2013}.

@@

	In summary, we have found that a single-body eroding in 2D
        Stokes flow converges to a terminal form characterized by nearly
        uniform shear stress along its surface. The final shape is
        fairly slender, with an aspect ratio of 2.7, and distinguished
        by  corners of opening angle $102^{\circ}$ at the front and
        rear. This shape is closely related to the drag-minimizing
        profile found by Pironneau (1973) --- the geometry that
        minimizes drag in 3D Stokes flow subject to the constraint of
        fixed volume~\cite{pir1973}. Using variational principles,
        Pironneau showed that the drag-minimizing form has constant
        shear (or vorticity) along its surface. The resulting {\em
        axisymmetric} shape has an aspect ratio of 2.1 and front/rear
        opening-angles of $120^{\circ}$~\cite{pir1973, mit-spa2016}.
        Interestingly, 3D simulations of viscous erosion showed close
        resemblance between the shape formed by a single eroding body
        and this Pironneau form~\cite{mit-spa2016}. It was found that
        the eroding body does not converge {\em precisely} to the
        Pironneau shape because the long-time surface-stress
        distribution created by erosion is only {\em approximately}
        uniform. Rather than strict uniformity, variations in body
        curvature must be offset by slight variations in $\Vn$ for
        self-similar reduction~\cite{pir1973, mit-spa2016}. Pironneau's argument that the drag-minimizing form has constant surface stress applies to 2D as well. Therefore, the shape observed in our simulation is approximately the form that minimizes drag subject to fixed area, i.e.~the 2D counterpart to Pironneau's shape. How close this shape is to the true drag-minimizer is related to how close the stress distributions are to uniform, as can be seen in Fig.~\ref{shrink_intface}(b).

@@

\section{Results: Multi-body erosion}
\label{s:MultiResults}

@@

Briefly, to validate the multi-body simulations with this new
fixed-pressure-drop condition, we report a convergence test in Table
\ref{convtab}. In this test, we simulate the erosion of 20 bodies to a
stopping time of $t_s = 4 \times 10^{-3}$. This stopping time is 24\% of
the time required for {\em all} bodies to vanish, and, in fact, a few of
the bodies will have already vanished by $t_s$. To assess error, we
measure the aggregate $L^2$-difference in the shape of {\em all} of the
bodies, comparing simulations of successive temporal resolution. Note
that this metric is sensitive to numerical errors in any of the
simulated bodies. The table confirms that our method retains
second-order accuracy in time, thus validating our rescaling procedure
and confirming that multi-body interactions are handled correctly by the Stokes solver. The last column of the table shows the computational time of each simulation, demonstrating a linear increase with temporal resolution. Naturally, these 20-body simulations require significantly more CPU time than do the single-body simulations.

@@

\subsection{Multi-body results}

With the validation complete, we now discuss the emergent physics of
multi-body erosion revealed by our simulations. We begin with a relatively simple case of 6 eroding bodies, as this will allow us to identify key principles at work in more complex cases (e.g.~the 50-body simulation in Fig.~\ref{fig:50bodies}). Figure~\ref{fig:06bodies} shows the simulated erosion of 6 bodies, each initial circles of various sizes and positions. Over time, erosion not only diminishes the size of the bodies, but also alters their shapes considerable. As in the single-body simulations, corner-like features develop, but not in locations that are easily predictable. Rather, when and where these corners form depends on how neighboring bodies interact with one another as mediated by the Stokes flow.

@@

%^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
\begin{figure}%[htbp]
\begin{center}
\includegraphics[width = 0.90 \textwidth]{./figs/mbodyplots.pdf}
\caption{\label{fig:mbodyplots} 
Multi-body simulation results: black curves correspond to the 6-body simulation and gray to the 50-body simulation. (a) The area fraction of the eroding bodies versus time. (b) The incoming flow rate $\umax$ versus time. The fixed-pressure-drop condition causes $\umax$ to increase as bodies erode. (c) The total drag exerted by all bodies. Because $\umax$ increases as the bodies erode, the drag remains nearly constant throughout much of the simulation. In the very last moments, the drag drops suddenly to zero. (d) Normalizing the drag by $\umax$ provides gives an estimate of how much resistance the porous matrix provides. The resistance decreases rapidly as the bodies erode.
}
\end{center}
\end{figure}
 %^^^^^^^^^^^^^^^^^^^^^^^^^^^^^^%
% Figure generated from data file 50circ512p5, 
%which uses 50circ512.in with epsfac = 30, sigfac = 10, dt = 1e-4, fixpdrop = 1

To further quantify these observations, Fig.~\ref{fig:mbodyplots} shows
several measurements taken from the multi-body simulations. In all cases, the black curves correspond to the above 6-body simulation and gray curves to the 50-body simulation from Fig.~\ref{fig:50bodies}. First, Fig.~\ref{fig:mbodyplots}(a) shows the fraction of area occupied by the solid bodies as it varies in time. In the 6-body simulation, the initial configuration comprises about 40\% of the domain area, and this percentage steadily decreases as the bodies erode. The 50-body simulation shows a similar trend.
